### 2016-08-12 Plos-one-manuscript/latex/manuscript.tex
update
added new figure updated tables

\begin{figure}
\caption{
{\bf Photos of pipette.}  The pipette is composed of three printed parts, a 1 mL syringe and some additional hardware.  
}
\label{fig2}
% Ideally: Photo showing assembled pipette as well as parts
\end{figure}

@@

% Please add the following required packages to your document preamble:
% \usepackage{multirow}
\begin{table}[]
\centering
\caption{
\bf{Comparison of error between the printed and commercially produced pipette}}
\begin{tabular}{llllll}
                  Volume &   & Systematic error &  & Random error & \\
                  \hline
\multirow{2}{*}{10 $\mu$L} & printed & 2.17 \% & $\pm$0.217$\mu$L  & 1.96\% & $\pm$0.196$\mu$L   \\
                  & commercial & 3\% & $\pm$0.3$\mu$L  & 1\% & $\pm$0.1$\mu$L  \\
                  \hline
\multirow{2}{*}{20 $\mu$L} & printed  & 0.33\% & $\pm$0.066$\mu$L & 1.18 \% & $\pm$0.236$\mu$L \\
                  & commercial & 2.50\% & $\pm$0.5$\mu$L & 0.70\% & $\pm$0.14$\mu$L \\
                  \hline
\multirow{2}{*}{50 $\mu$L} & printed & 1.17\% & $\pm$0.585$\mu$L & 0.50\% & $\pm$0.25$\mu$L \\
                  & commercial & 1\% & $\pm$0.5$\mu$L & 0.30\% & $\pm$0.15$\mu$L \\
                  \hline
\multirow{2}{*}{200 $\mu$L} & printed & 2.52\% & $\pm$5.04$\mu$L & 0.69\% & $\pm$1.38$\mu$L  \\
                  & commercial & 0.6\% & $\pm$1.2$\mu$L & 0.20\% & $\pm$0.4$\mu$L
\end{tabular}
\begin{flushleft} Error assessed for average measured volume by weight of water compared with published specifications of commercial pipette. [Alos compare to data taken with commercial pipettes in our lab]
\end{flushleft}
\label{table1}
\end{table}

The novice user data demonstrates that the pipette set point is user friendly and is capable of accurate measurements without validating with a scale (Figure~\ref{fig3}).

\begin{table}[]
\centering9
\caption{
\bf{Novice Users' first attempt}}
\begin{tabular}{llll}
Target volume & Average $\pm$ SD & Systematic error  & Random error\\
\hline
10 $\mu$L         & 7.6 $\pm$ 3.3     & -23.80\% & 9.95\% \\
\hline
20 $\mu$L         & 18.1 $\pm$ 4.4   & -9.60\%   & 6.66\% \\
\hline
50 $\mu$L         & 45.3 $\pm$ 4.6   & -9.48\%   & 2.75\% \\
\hline
200 $\mu$L       & 185.2 $\pm$ 5.6 & -7.43\%   & 0.84\%
\end{tabular}
\begin{flushleft} Error assessed for average measured volume by weight of water compared with published specifications of commercial pipette.
\end{flushleft}
\label{table2}
\end{table}

>>>>

\begin{figure}
\caption{
{\bf CAD rendering of printable parts.}  Three parts are printed: the body, plunger shaft, and luer-lock adapter for pipette tips.
}
\label{fig2}
% Ideally: cad rendering showing the design and function of the pipette. 
% a) Un-assembled whole parts next to their cross-sections.  
% b) Assembly next to crossection
% c) close up of how the locking groove/mechanism works
% d) cross-section showing the two positions of the plunger, locked at the goove and stopped at the screw 
\end{figure}

\begin{figure}
\caption{
{\bf Photos of pipette.}  The pipette is composed of three printed parts, a 1 mL syringe and some additional hardware.  
}
\label{fig3}
% Ideally: Photo showing assembled pipette as well as parts
\end{figure}

@@

% Please add the following required packages to your document preamble:
% \usepackage{multirow}
\begin{table}[!ht]
\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\caption{ISO 8655 for 100-1000 uL comparing a commercial pipette with our printed pipette used with existing 3 mL syringe scale and an adjusted scale}
\label{table1}
\begin{tabular}{lllllll}
        &                       & Mean   & Systematic Error & \% Sys. err. & Random Error & \% Rand. err. \\
1000 uL & ISO 8655, 100-1000 uL & 1000    & 8.00             & 0.80         & 3.00         & 0.30          \\
        & Commercial Pipette    & 1002.98 & 2.98             & 0.30         & 1.72         & 0.17          \\
        & Printed Pipette       & 949.29  & -50.71           & -5.07        & 0.60         & 0.06          \\
        & Printed Pipette Scale & 1003.57 & 3.57             & 0.36         & 0.89         & 0.09          \\
        &                       &         &                  &              &              &               \\
500 uL  & ISO 8655, 100-1000 uL & 500     & 8.00             & 1.60         & 3.00         & 0.60          \\
        & Commercial Pipette    & 503.67  & 3.67             & 0.73         & 0.49         & 0.10          \\
        & Printed Pipette       & 475.99  & -24.01           & -4.80        & 4.75         & 1.00          \\
        & Printed Pipette Scale & 503.62  & 3.62             & 0.72         & 1.64         & 0.33          \\
        &                       &         &                  &              &              &               \\
200 uL  & ISO 8655, 100-1000 uL & 200     & 8.00             & 4.00         & 3.00         & 1.50          \\
        & Commercial Pipette    & 204.61  & 4.61             & 2.30         & 0.15         & 0.07          \\
        & Printed Pipette       & 186.55  & -13.45           & -6.72        & 1.31         & 0.70          \\
        & Printed Pipette Scale & 201.87  & 1.87             & 0.94         & 1.47         & 0.73          \\
        &                       &         &                  &              &              &               \\
100 uL  & ISO 8655, 100-1000 uL & 100     & 8.00             & 8.00         & 3.00         & 3.00          \\
        & Commercial Pipette    & 104.29  & 4.29             & 4.29         & 1.65         & 1.58          \\
        & Printed Pipette       & 94.02   & -5.98            & -5.98        & 4.81         & 5.12          \\
        & Printed Pipette Scale & 101.00  & 1.00             & 1.00         & 1.05         & 1.04         
\end{tabular}
%\begin{flushleft} Table notes Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec pellentesque metus tortor nec nisl. Ut ornare mauris tellus, vel dapibus arcu suscipit sed.
%\end{flushleft}
\end{adjustwidth}
\end{table}

\begin{table}[!ht]
\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\caption{ISO 8655 for 30-300 uL comparing a commercial pipette with our printed pipette used with existing 3 mL syringe scale and an adjusted scale}
\label{table2}
\begin{tabular}{lllllll}
       &                       & Mean   & Systematic Error & \% Sys. err. & Random Error & \% Rand. err. \\
300 uL & ISO 8655, 30-300 uL   & 300    & 4.00             & 1.33         & 1.50         & 0.50          \\
       & Commercial Pipette    & 301.19 & 1.19             & 0.40         & 0.53         & 0.18          \\
       & Printed Pipette       & 286.91 & -13.09           & -4.36        & 0.42         & 0.15          \\
       & Printed Pipette Scale & 299.11 & -0.89            & -0.30        & 0.48         & 0.16          \\
       &                       &        &                  &              &              &               \\
200 uL & ISO 8655, 30-300 uL   & 200    & 4                & 2            & 1.5          & 0.75          \\
       & Commercial Pipette    & 200.06 & 0.06             & 0.03         & 0.46         & 0.23          \\
       & Printed Pipette       & 193.40 & -6.60            & -3.30        & 2.86         & 1.48          \\
       & Printed Pipette Scale & 200.57 & 0.57             & 0.28         & 0.86         & 0.43          \\
       &                       &        &                  &              &              &               \\
50 uL  & ISO 8655, 30-300 uL   & 50     & 4                & 8            & 1.5          & 3             \\
       & Commercial Pipette    & 49.02  & -0.98            & -1.96        & 0.10         & 0.20          \\
       & Printed Pipette       & 49.62  & -0.38            & -0.76        & 1.26         & 2.53          \\
       & Printed Pipette Scale & 48.73  & -1.27            & -2.54        & 1.11         & 2.27          \\
       &                       &        &                  &              &              &               \\
30 uL  & ISO 8655, 30-300 uL   & 30     & 4                & 13.3         & 1.5          & 5             \\
       & Commercial Pipette    & 29.08  & -0.92            & -3.06        & 0.09         & 0.31          \\
       & Printed Pipette       & 29.22  & -0.78            & -2.59        & 0.31         & 1.07          \\
       & Printed Pipette Scale & 27.78  & -2.22            & -7.41        & 1.37         & 4.93          \\
       &                       &        &                  &              &              &               \\
20 uL* & ISO 8655, 30-300 uL   & 20     & 4                & 20           & 1.5          & 7.5           \\
       & Commercial Pipette    & NA     & NA               & NA           & NA           & NA            \\
       & Printed Pipette       & 18.70  & -1.30            & -6.48        & 0.38         & 2.01          \\
       & Printed Pipette Scale & 17.94  & -2.06            & -10.29       & 1.87         & 10.42         \\
       &                       &        &                  &              &              &               \\
10 uL* & ISO 8655, 30-300 uL   & 10     & 4                & 40           & 1.5          & 15            \\
       & Commercial Pipette    & NA     & NA               & NA           & NA           & NA            \\
       & Printed Pipette       & 11.95  & 1.95             & 19.52        & 0.73         & 6.08          \\
       & Printed Pipette Scale & 7.64   & -2.36            & -23.64       & 0.38         & 4.92         
\end{tabular}
\begin{flushleft} * The 20 uL and 10 uL volumes are out of the range in this case but we wanted to demonstrate that the pipette is capable of even smaller volumes.
\end{flushleft}
\end{adjustwidth}
\end{table}
